### 2020-09-14 LaTeX/sections/abstract.tex
more edits

\begin{abstract}

Abstract goes here

\end{abstract}

>>>>

\begin{abstract}
Order-driven exchanges on Ethereum tend to operate in a fully centralized fashion, or with some functionality performed on-chain (\eg loading accounts, order cancelation) and some off-chain functionality (\eg matching orders). Fully on-chain solutions have a superior threat model and were experimented with in the early days of Ethereum, but they have been largely abandoned for performance reasons. As blockchain performance continues to improve (both in research and in practice) and on-chain dealer-based exchanges like Uniswap (an alternative to order-based exchanges) rise in popularity, it seems to be an ideal time to revisit the idea of a fully on-chain order-driven exchange and benchmark what is possible performance-wise. We design and optimize an Ethereum-based call market exchange, \cm, and conduct a variety of experiments to show the current benchmark is around one hundred trade executions per block. We also explore numerous extensions for further improvements.
\end{abstract}

### 2020-09-14 LaTeX/sections/paper.tex
more edits

% = = = = = = = = = = = = = = = = =

\paragraph{Contributions.}

We design and implement \cm, a fully on-chain call market in Solidity---a high-level programming language for Ethereum. We choose Ethereum as a `hostile' environment for an orderbook: Ethereum is public (strongest adversary) and slow (lower-bound benchmark) relative to more scalable blockchains, including the anticipated Ethereum 2.0. \cm is intended as a simple module that developers can modify as they choose. By adding \cm to an ERC20 (or similar) token contract, everything that is needed for buying/selling tokens is immediately available on chain without involving any third party exchanges. \cm is non-custodial, transparent, and mitigates front-running attacks that are generally possible on-chain.

@@

@@

\paragraph{Execution systems.} There are three main approaches to arranging a trade. In a \emph{quote-driven} market, a dealer uses their own inventory to offer a price for buying or selling an asset. In a \emph{brokered exchange}, a broker finds a buyer and seller. In an \emph{order-driven} market, offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an orderbook. Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the orderbook (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch like an auction.

@@

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

@@

% = = = = = = = = = = = = = = = = =
\begin{enumerate}

%---------+++++++++++++++++++-----------------

\item\textbf{{Heap with Dynamic Array.}} A heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap. All the nodes of tree are in a specific order and the root of the tree always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively). We implemented a priority queue with a heap that stores its data in a dynamically-sized array.

%---------+++++++++++++++++++-----------------

\item\textbf{{Heap with Static Array.}} A heap can be also represented by a Solidity storage array in which the storage is statically allocated. To do this, we pass the required size of the array as a constructor parameter to the priority queue smart contract.

%---------+++++++++++++++++++-----------------

\item\textbf{{Heap with Mapping.}} In the above implementations, the heap stores the entire order (as a struct) in the heap. In this variant, we store the order struct in a Solidity mapping and store the mapping's key in the heap.

%---------+++++++++++++++++++-----------------

\item\textbf{{Linked List.}} In this variant, we insert a new element into its correct position (based on its price) when running enqueue. The PQ itself stores elements in a linked list (enabling us to efficiently insert a new element between two existing elements). Solidity is described as object-oriented but the equivalent of an object is an entire smart contract. Therefore an object-oriented linked list must either (i) create each node in the list as a struct---but this is not possible as Solidity does not support recursive structs---or (ii) make every node in the list its own contract. The latter option seems wasteful and unusual, but we try it out anyways. Thus each node is its own contract and contains the order data and a pointer to the address of the next contract in the list.

%---------+++++++++++++++++++-----------------

\item\textbf{{Linked List with Mapping.}} Finally, we try a variant of a linked list using a Solidity mapping. The value of the mapping is a struct with order data and the key of the next (and previous) node in the list. The contract stores the key of the first node (head) in the list.

%---------+++++++++++++++++++-----------------

\end{enumerate}
% = = = = = = = = = = = = = = = = =
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

@@

% = = = = = = = = = = = =random_insertion Figure = = = = = = = = = = = = =  %

@@

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
%  = = = = = = Table 2 (dequeue) Conversions = = = = = = %
%
%As of July 2020,  $1 gas = 56\times10^{-9} ether$\footnote{https://ethstats.net/} and 1 ether = \$238.33\footnote{https://coinmarketcap.com/}.
%
%$Transaction cost (eth) = GasUsed (unit) \times Gas Price (eth)$ 
%
%%  = = = = = = Transaction Costs in eth = = = = = = %
%
%Heap with Dynamic Array:    		$2,518,131 \times 56\times10^{-9} = 141,015,336\times 10^{-9}$
%Heap with Dynamic Array:     		$1,385,307 \times 56\times10^{-9} = 77,577,192\times 10^{-9}$
%Heap with Mapping:              		$2,781,684 \times 56\times10^{-9} = 155,774,304\times 10^{-9}$
%Linked List:						$557,085 \times 56\times10^{-9} = 	31,196,760\times 10^{-9}$
%Linked List with Mapping:			$731,514 \times 56\times10^{-9} = 	40,964,784\times 10^{-9}$
%
%%  = = = = = = Transaction Costs in USD = = = = = = %
%
%Heap with Dynamic Array:    		$141,015,336\times 10^{-9} \times 238.33 = \$33.60$
%Heap with Dynamic Array:     		$77,577,192\times 10^{-9} \times 238.33 = \$18.48$
%Heap with Mapping:              		$155,774,304\times 10^{-9} \times 238.33 = \$37.12$
%Linked List:						$31,196,760\times 10^{-9} \times 238.33 = \$7.43$
%Linked List with Mapping:			$40,964,784\times 10^{-9} \times 238.33 = \$9.76$
%
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

@@

%---------+++++++++++++++++++-----------------
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

%  = = = = = = Table 3 (cleaning.tex) Conversions = = = = = = %

%As of July 2020,  $1 gas = 56\times10^{-9} ether$\footnote{https://ethstats.net/} and 1 ether = \$238.33\footnote{https://coinmarketcap.com/}.
%
%$Transaction cost (eth) = GasUsed (unit) \times Gas Price (eth)$ 
%
%%  = = = = = = Transaction Costs in eth = = = = = = %
%
%Linked List with \texttt{SELFDESTRUCT}:     				$557,085 \times 56\times10^{-9} =  31,196,760\times 10^{-9}$  
%Linked List w/o \texttt{SELFDESTRUCT}:     				$721,370 \times 56\times10^{-9} =  40,396,720\times 10^{-9}$ 
%Linked List with Mapping and \texttt{DELETE}:    			$731,514 \times 56\times10^{-9} =  40,964,784\times 10^{-9}$ 
%Linked List with Mapping and w/o \texttt{DELETE}: 		$334,689 \times 56\times10^{-9} =  18,742,584\times 10^{-9}$ 
%
%%  = = = = = = Transaction Costs in USD = = = = = = %
%
%Linked List with \texttt{SELFDESTRUCT}:     				$31,196,760\times 10^{-9}  \times 238.33 = \$7.43$
%Linked List w/o \texttt{SELFDESTRUCT}:     				$40,396,720\times 10^{-9} \times 238.33 = \$9.62$
%Linked List with Mapping and \texttt{DELETE}:    			$40,964,784\times 10^{-9}  \times 238.33 = \$9.76$
%Linked List with Mapping and w/o \texttt{DELETE}: 		$18,742,584\times 10^{-9} \times 238.33 = \$4.46$
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

%Although the \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and refunds 24000 gas to the caller.

@@

% = = = = = = = = = = = = = Implementatiion = = = = = = = = = = = = = = = = = = =  %

@@

%GitHub repo:  \footnote{\CallMarketRepo}
% = = = = = = = = = = = = = = = = = = = = =Call market operations Table = = = = = = = = = = = =  = = = = = =  %
\begin{table}[t]
\begin{tabular}{|l|l|}
\hline
\multicolumn{1}{|c|}{\textbf{Operation}} & \multicolumn{1}{c|}{\textbf{Description}}                            			\\ \hline

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	DepositToken()                           & Deposits ERC20 standard compliant tokens in the call market contract \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	DepositEther()                           	& Deposits Ethers in the call market contract                         			 \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	OpenMarket()                             & Opens the market                                                    					 \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	CloseMarket()                            & Closes the market                                                    					\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	SubmitBid()                              & Inserts the upcoming bid order messages inside the priority queue    \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	SubmitAsk()                              & Inserts the upcoming ask order messages inside the priority queue    \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	MatchOrders()                           & Matches the orders against each other                                			\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	ClaimTokens()                           & Transfers collateral tokens back to the trader                       			\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	ClaimEther()                             & Transfers collateral Ethers back to the trader                       			\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
\end{tabular}
\caption{\footnotesize{Primary operations of the call market smart contract.}
\label{tab:callmarket_functions}}
\end{table}

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

Our design \cm is intended as a module that developers can modify as they choose---thus we tried to simplify the design at every step to make it highly extensible but still functional without any extensions. A call market will open for a specified period of time during which it will accept orders. Orders are added to a PQ. Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block). This is akin to how a crossing network operates in traditional finance (\ie \textblue{some explanation}). We keep the design simple by not allowing cancellations. Because markets are relatively short-lived, cancelations require a second transaction (and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}), orders simply expire when the market call period ends.

@@

 \subsection{Performance}

@@

\textblue{Optimize for closing market, even at cost of higher submission.}

@@

\section{Call Market Different Design and Implementation Details }

\subsection{Front-running} \label{sec:front}
% Front running -> drop trades, move to next block, can't front-run
% Take 1000 trades over a window of time -> shuffle -> what is different between A and B?u
% No price improvement changes people waiting to trade?

>>>>

\paragraph{Contributions.} We design and implement \cm, a fully on-chain call market in Solidity---a high-level programming language for Ethereum. We choose Ethereum as a `hostile' environment for an orderbook: Ethereum is public (strongest adversary) and slow (lower-bound benchmark) relative to more scalable blockchains, including the anticipated Ethereum 2.0. \cm is intended as a simple module that developers can modify as they choose. By adding \cm to an ERC20 (or similar) token contract, everything that is needed for buying/selling tokens is immediately available on chain without involving any third party exchanges. \cm is non-custodial, transparent, and mitigates front-running attacks that are generally possible on-chain.

@@

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

@@

\paragraph{Execution systems.} There are three main approaches to arranging a trade~\cite{Har03}. In a \emph{quote-driven} market, a dealer uses their own inventory to offer a price for buying or selling an asset. In a \emph{brokered exchange}, a broker finds a buyer and seller. In an \emph{order-driven} market, offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an orderbook. Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the orderbook (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch like an auction.

@@

\paragraph{Other Literature.}
% Madiba -> pulp.bib
% Velocity, 
% FuturesMex~\cite{massacci2018futuresmex}
% Findel 
% Libra~\cite{mavroudis2019libra}
% Arwen
% Tesseract (SGX-exchange)~\cite{bentov2017tesseract}
% Christopher Thorpe

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

@@

\begin{enumerate}

\item \textbf{Heap with Dynamic Array.} A heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap. All the nodes of tree are in a specific order and the root of the tree always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively). We implemented a priority queue with a heap that stores its data in a dynamically-sized array.

\item \textbf{Heap with Static Array.} A heap can be also represented by a Solidity storage array in which the storage is statically allocated. To do this, we pass the required size of the array as a constructor parameter to the priority queue smart contract.

\item \textbf{Heap with Mapping.} In the above implementations, the heap stores the entire order (as a struct) in the heap. In this variant, we store the order struct in a Solidity mapping and store the mapping's key in the heap.

\item \textbf{Linked List.} In this variant, we insert a new element into its correct position (based on its price) when running enqueue. The PQ itself stores elements in a linked list (enabling us to efficiently insert a new element between two existing elements). Solidity is described as object-oriented but the equivalent of an object is an entire smart contract. Therefore an object-oriented linked list must either (i) create each node in the list as a struct---but this is not possible as Solidity does not support recursive structs---or (ii) make every node in the list its own contract. The latter option seems wasteful and unusual, but we try it out anyways. Thus each node is its own contract and contains the order data and a pointer to the address of the next contract in the list.

\item \textbf{Linked List with Mapping.} Finally, we try a variant of a linked list using a Solidity mapping. The value of the mapping is a struct with order data and the key of the next (and previous) node in the list. The contract stores the key of the first node (head) in the list.

\end{enumerate}

@@

@@

@@

@@

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

@@

%GitHub repo:  \footnote{\CallMarketRepo}

\input{tables/functions.tex}

\cm is intended as a module that developers can modify as they choose---thus we tried to simplify the design at every step to make it highly extensible but still functional without any extensions. A call market will open for a specified period of time during which it will accept orders. Orders are added to a PQ. Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block). We keep the design simple by not allowing cancellations. Because markets are relatively short-lived, cancelations require a second transaction, and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}, orders simply expire when the market call period ends.

@@

 \subsection{Measurements}

@@

\subsection{Security Analysis} \label{sec:front}

\paragraph{Front-running.} 
% Front running -> drop trades, move to next block, can't front-run
% Take 1000 trades over a window of time -> shuffle -> what is different between A and B?u
% No price improvement changes people waiting to trade?

\paragraph{Contract Security.} We used two security audit tools, \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck},\footnote{https://tool.smartdec.net}, on \cm to find vulnerabilities and bad practices. We received 100\% success rate in a total of 67 audits performed by considering 'Informational' checks as 'passed'.

@@

\section{Design alternatives and extensions}

\subsection{Resolving ties}

\subsection{Price level / volume level}
